On the discovery of K-enhanced and Mg-depleted stars throughout the Milky Way\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}

### 2018-05-06 article/msculled.tex
pre-change push

A targeted search looking for [K/Fe] in RGB and main sequence turn-off stars in other clusters (NGC 6752, NGC 6121, NGC 1904, 47 Tuc, NGC 6397, NGC 7099, and $\omega$ Centauri) and field stars concluded that all K abundance ratios fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}. 
NGC 2808 is the only cluster, other than NGC 2419, where an anticorrelation between Mg and K has been observed. All four of NGC 2808's known Mg-depleted stars show an anti-correlation with K \citep{mucciarelli2015}, although the amplitude of these abundance ratios is far weaker than those found in NGC 2419. The fact that the Mg-K anti-correlation is apparently confined to these two globular clusters implies either a small population of unusual polluter stars, or a single extremely massive polluter star. If it were the cumulative effect of many pollution events that was responsible for the signal, it would be expected that the anomalous abundances would be common among globular clusters.

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{posterchild.png}
    \caption{Normalised \lamost\ spectrum for the Mg-depleted and K-enhanced candidate J034458.82+592955.1. The data are shown in black and the best-fitting data-driven model from \tc\ is in red. We zoom in around the magnesium triplet and potassium doublet, which we used to identify Mg--K candidates. Note that $[\alpha/{\rm Fe}]$ is a label in \tc\ model used and J034458.82+592955.1 shows Mg depletions relative to the estimated [$\alpha$/Fe] value.}
    \label{posterchild}
\end{figure*}

>>>>

A targeted search looking for [K/Fe] in RGB and main sequence turn-off stars in other clusters (NGC 6752, NGC 6121, NGC 1904, NGC 104, NGC 6397, NGC 7099, and $\omega$ Centauri) and field stars concluded that all K abundance ratios fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}, and no correlations between Mg and K were observed. Recent work by \cite{cerniauskas201747tuc} searched for unusual abundance patterns in Mg and K in NGC 104 through deriving abundances using 2df/HERMES spectra, and a more comprehensive study involving over 400 stars in NGC 104, NGC 6752, and NGC 6809 by \cite{mucciarelli2017K} using FLAMES spectra \citep{cerniauskas201747tuc} both found no correlations between Mg and K, and no significant intrinsic spreads in either Mg or K.

NGC 2808 is the only cluster, other than NGC 2419, where an anticorrelation between Mg and K has been observed. All four of NGC 2808's known Mg-depleted stars show an anti-correlation with K \citep{mucciarelli2015}, although the amplitude of these abundance ratios is far weaker than those found in NGC 2419. The fact that the Mg-K anti-correlation is apparently confined to these two globular clusters implies either a small population of unusual polluter stars, or a single extremely massive polluter star. If it were the cumulative effect of many pollution events that was responsible for the signal, it would be expected that the anomalous abundances would be common among globular clusters.

@@

\begin{figure*}
\centering
\begin{subfigure}{1\textwidth}
\centering
\includegraphics[width=\textwidth=1]{posterchild.png}
\caption{Mg-depleted, K-enhanced candidate J034458.82+592955.1.}
\end{subfigure}

\begin{subfigure}{1\textwidth}
\centering
\includegraphics[width=\textwidth=1]{postermimic.png}
\caption{Mg-normal, K-normal star J163532.2+238131.54. }
\end{subfigure}

\caption{Normalised \lamost\ spectrum for the Mg-depleted and K-enhanced candidate J034458.82+592955.1 and for the comparable star J163532.2+238131.54. J163532.2+238131.54 was selected by minimising the similarity norm defined as $n=(\frac{\Delta \text{T}_{\text{eff}}}{1000})^2 +\Delta \text{logg} ^2 + \Delta \text{[Fe/H]}^2$. The data are shown in black and the best-fitting data-driven model from \tc\ is in red. We zoom in around the magnesium triplet and potassium doublet, which we used to identify Mg--K candidates. Note that $[\alpha/{\rm Fe}]$ is a label in \tc\ model used and J034458.82+592955.1 shows Mg depletions relative to the estimated [$\alpha$/Fe] value.}
\label{meshindepvisc}
\end{figure*}
